Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-09-12 doc/main_jfm.tex

This study presents a continuum coarse-grained model for JP vesicles
that focuses on the hydrophobic interactions between coarse-grained
lipids and hydrodynamic interactions. In contrast to molecular dynamic
simulations, the hydrophobic interactions exhibit the self-assembly
property of the lipid bilayer membrane. The proposed energy potential
combined with the mobility problem for rigid body motions captures
membrane mechanics including deformations, stretching modulus, and the
permeability of a JP membrane. This work is highly applicable with
fields in material science and condensed matter physics such as Janus
colloids~(\cite{Bradley2017,Mallory2017}) and the setup can be tuned to
match experimental results such as the morphology of colloid
surfactants~(\cite{Bradley2016}).

Integral equation methods are used to solve the mobility problem and the
previously introduced HAP model that determines the forces and torques
of the individual rigid bodies. In addition to the HAP forces and
torques, we impose a short-range repulsion to avoid unphysical contact.
Our method requires calculations of the hydrodynamic stress tensor, and
this is leads to examinations of the membrane permeability constant $P$
and the membrane stretching modulus $K_A$. With the use of suitable
parameters, the numerical results yield good qualitative phenomena such
as a tank-treading JP vesicle. The reduced area $A^*$ decreases as the
shear rate increases and we measure the equilibrium reduced area for
various shear rates. The results show that the total length of a JP
vesicle is conserved and the decay rate of the reduced area is
independent of the shear rate values  between $0.005$~ns$^{-1}$
and~$0.008$ ns$^{-1}$. Moreover, the proposed model can describe
membrane rupture in high shear rates. Therefore, our methods can be
applied to vesicles undergoing topological changes which is not
difficult to simulate when using a continuum model that represents
vesicles as closed and continuous curves.

Our coarse-grained model is also able to calculate inter-monolayer
friction. The inter-monolayer friction coefficients are determined by
calculating the tangential friction force and slip velocities with
respect to the bilayer midplane. The resulting friction coefficients $b$
are about one order of magnitude smaller than those reported
by~\cite{denOtter2007}, and this discrepancy is partially due to the
granularity of the model. In addition, the coarse-graining level of the
JP vesicle has a much larger length scale than molecular dynamics
simulations, and the repulsive force creates gaps between Janus
particles where the error in slip velocities accumulates over time.

We also study the spatial migration of a JP vesicle suspended in a
parabolic flow. The chosen parameter values results in an asymmetric
slipper shape. A qualitative agreement has been made comparing with the
two-dimensional inextensible membrane in continuum modeling
simulations~(\cite{Kaoui09, dan-vla-mis2009, cou-kao-pod-mis2008}). The
initial reduced area of the JP vesicle is $A^* \approx 1$ and the
equilibrium reduced area is $A^*=0.9$. An interesting result of the JP
vesicle is that the mean $y$-position oscillates toward the center of
the Poiseuille flow and this may be caused by the granularity of the JP
vesicle and choices of the model parameters.

We compare two JP vesicles with a similar setup using a continuum model.
A comparison of the vesicle shapes and the streamlines demonstrate
remarkable similarities. The two overlapping trajectories of the JP
vesicles' centroids in a shear flow evolve as expected when the two
centroids are initialized on the same horizontal level. We also observe
a rotating behavior that is observed for models involving vesicle
adhesion~(\cite{qua-vee-you2019}). The hydrophobic action and the
repulsive potential lead to this adhesive effect when two JP bilayers
are within a short distance. We also perform four simulations of two JP
vesicles suspended in an extensional flow. We vary the initial vertical
displacement of the vesicles' centroids and obtain similar results to
the continuum model.

\todo[inline]{Bryan left off here}
Our future goal is to extend the current framework to a
three-dimensional JP vesicle system. The further implementation of
adding a fast algorithms such as the fast multipole method is also a
practical approach. One ongoing work is to add thermal fluctuations onto
Janus particles to obtain Brownian dynamics is crucial for obtaining
membrane diffusion. Having a more physical boundary conditions on JP
boundaries with experimental data is a reasonable direction and the
future comparison with the laboratory experiments can be accomplished.

>>>>

This study presents a coarse-grained model for JP vesicles that focuses
on the hydrophobic interactions between coarse-grained lipids and
hydrodynamic interactions. In contrast to molecular dynamic simulations,
the hydrophobic interactions exhibit the self-assembly property of the
lipid bilayer membrane. The proposed energy potential combined with the
mobility problem for rigid body motions captures membrane mechanics
including deformations, stretching modulus, and permeability of a JP
membrane. This work is highly applicable with fields in material science
and condensed matter physics such as Janus
colloids~(\cite{Bradley2017,Mallory2017}) and the setup can be tuned to
match experimental results such as the morphology of colloid
surfactants~(\cite{Bradley2016}).

Integral equation methods are used to solve the mobility problem and the
previously introduced HAP model. We describe a method to calculate the
hydrophobic forces and torques on each individual rigid body that avoids
singular integrals. In addition to the HAP forces and torques, we use a
short-range repulsion to avoid unphysical contact. Our method requires
calculations of the hydrodynamic stress tensor, and these are used to
estimate the membrane permeability constant $P$ and the membrane
stretching modulus $K_A$. With the use of suitable parameters, the
numerical results yield qualitative phenomena such as a tank-treading JP
vesicle. The reduced area $A^*$ decreases as the shear rate increases
and we measure the equilibrium reduced area for various shear rates. The
results show that the total length of a JP vesicle is conserved and the
decay rate of the reduced area is independent of the shear rate values
between $0.005$~ns$^{-1}$ and~$0.008$~ns$^{-1}$. Moreover, the proposed
model can describe membrane rupture in high shear rates. Therefore, our
method can be applied to vesicles undergoing topological changes which
is difficult to simulate when using a continuum model that represents
vesicles as closed and continuous curves.

Our coarse-grained model is also able to calculate inter-monolayer
friction. The inter-monolayer friction coefficient is determined by
calculating the tangential friction force and slip velocities with
respect to the bilayer midplane. The resulting friction coefficients are
about an order of magnitude smaller than those reported
by~\cite{denOtter2007}, and this discrepancy is partially due to the
granularity of our model. In addition, the coarse-graining level of the
JP vesicle has a much larger length scale than molecular dynamics
simulations, and the repulsive force creates gaps between Janus
particles where the error in slip velocities accumulates over time.

We also study the spatial migration of a JP vesicle suspended in a
parabolic flow. The chosen parameter values result in an asymmetric
slipper shape. While the initial reduced area of the JP vesicle is $A^*
\approx 1$, the equilibrium reduced area is $A^*=0.9$. A qualitative
agreement is made by comparing the JP vesicle shape with the
two-dimensional inextensible membrane in continuum modeling
simulations~(\cite{Kaoui09, dan-vla-mis2009, cou-kao-pod-mis2008}). An
interesting result of the JP vesicle is that $y$-coordinate of the
centroid oscillates at a value slightly above the center of the
Poiseuille flow. This may be caused by the granularity of the JP vesicle
and choices of the model parameters.

We compare setups of two JP vesicles and two vesicles described with a
continuum model. A comparison of the vesicle shapes and the streamlines
demonstrate remarkable similarities. The two overlapping trajectories of
the JP vesicles' centroids in a shear flow evolve as expected when the
two centroids are initialized on the same horizontal level. We also
observe a rotating behavior that is observed for models involving
vesicle adhesion~(\cite{qua-vee-you2019}). The hydrophobic action and
the repulsive potential lead to this adhesive effect when two JP
bilayers are sufficiently close. We also perform four simulations of two
JP vesicles suspended in an extensional flow. We vary the initial
vertical displacement of the vesicles' centroids and obtain similar
results to the continuum model.

Our future goals include extending the current framework to a
three-dimensional JP vesicle system. This will require additional
algorithmic implementation including a fast summation method such as the
fast multipole method. Another research direction is to introduce
thermal fluctuations into the model. This will result in Janus particles
that include Brownian motion, and this is critical to understand
membrane diffusion. Finally, a more physical boundary condition for the
HAP model will allow us to draw comparisons between computational and
laboratory experiments.
